以太坊：一种安全去中心化的通用交易账本 \\ {\smaller \textbf{EIP-150版本 (\YellowPaperVersionNumber{})}}

### 2017-08-09 Paper_Chinese.tex
update

上述是区块链的基本内容，这个模型不仅是以太坊的基础架构，还是迄今为止所有基于共识的去中心化交易系统的基础架构。

@@

In order to incentivise computation within the network, there needs to be an agreed method for transmitting value. To address this issue, Ethereum has an intrinsic currency, Ether, known also as {\small ETH} and sometimes referred to by the Old English \DH{}. The smallest subdenomination of Ether, and thus the one in which all integer values of the currency are counted, is the Wei. One Ether is defined as being $10^{18}$ Wei. There exist other subdenominations of Ether:
\par
\begin{center}
\begin{tabular}{rl}
\toprule
Multiplier & Name \\
\midrule
$10^0$ & Wei \\
$10^{12}$ & Szabo \\
$10^{15}$ & Finney \\
$10^{18}$ & Ether \\
\bottomrule
\end{tabular}
\end{center}
\par

Throughout the present work, any reference to value, in the context of Ether, currency, a balance or a payment, should be assumed to be counted in Wei.

>>>>

上述是区块链的基本内容，这个模型不仅是以太坊的基础，还是迄今为止所有基于共识的去中心化交易系统的基础。

@@

为了激励网络中的计算，需要定义一种转账方法。以太坊设计了一个内置货币以太币(Ether)，ETH是大家所熟知的符号，有时用 \DH{} 表示。以太币最小的面额是Wei(伟)，所有货币值都以Wei的整数倍记录。一个以太币被定义成位。一个以太币等于 $10^{18}$ Wei 。不同的面值如下表:

\par
\begin{center}
\begin{tabular}{rl}
\toprule
倍数 & 面值 \\
\midrule
$10^0$ & Wei(伟)) \\
$10^{12}$ & Szabo(萨博) \\
$10^{15}$ & Finney(芬尼) \\
$10^{18}$ & Ether(以太) \\
\bottomrule
\end{tabular}
\end{center}
\par

在整个工作中，任何涉及到价值、以太币相关的、货币、余额或者支付，都以Wei作为单位来计算。
